### 2013-07-24 doc/asplos14/overview.tex
small changes

\Grappa's design is motivated by two key observations of today's systems.
First, modern compute cores can execute hundreds of thousands of instructions
in the few microseconds that it takes for one RDMA read to complete. Second,
the injection rate of modern commodity networks is low and the bandwidth is
optimized for large messages. Given the frequent communication caused by high
degree of fine-grained random access in irregular applications, it is
necessary to both overlap communication with computation as much as possible
and to aggregate network messages efficiently. Providing these two properties
depend on exploiting large amounts of concurrency. Hence, \Grappa's
programming model focuses on enabling programmers to easily express
concurrency.

@@

GASNet~\cite{gasnet} is used as the
underlying mechanism for remote memory reads and writes using active message
invocations, with an off-the-shelf user-mode InfiniBand device driver
stack~\cite{OFED}. MPI is used for process setup and tear down.

>>>>

\Grappa's design is motivated by two key observations of today's systems.
First, modern compute cores can execute hundreds of thousands of instructions
in the few microseconds that it takes for one remote memory read to complete. Second,
the injection rate of modern commodity networks is low and the bandwidth is
optimized for large messages. Given the frequent communication caused by high
degree of fine-grained random access in irregular applications, it is
necessary to both overlap communication with computation as much as possible
and to aggregate network messages efficiently. Providing these two properties
depend on exploiting large amounts of concurrency. Hence, \Grappa's
programming model focuses on enabling programmers to easily express
concurrency.

@@

GASNet~\cite{gasnet} is used as the
underlying mechanism for bulk remote memory reads and writes using active message
invocations, with an off-the-shelf user-mode InfiniBand device driver
stack~\cite{OFED}. MPI is used for process setup and tear down.
